---
title: "Activity 2 - Accuracy estimations"
author: "Julie Vercelloni"
date: "29 March 2019"
output:
  html_document: default

---

<style>
table, td, th {
 border: none;
 padding-left: 1em;
 padding-right: 1em;
 min-width: 50%;
 margin-left: auto;
 margin-right: auto;
 margin-top: 1em;
 margin-bottom: 1em;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Using the table_final from Activity 1, we are now going to estimate your accuracy for reef image classifications. 

##Load the R libraries

```{r}
rm(list=ls())

julie <- Sys.info()["nodename"] == "SEF-PA00130783"

if (julie){
  .libPaths("C:\\Julie\\Rpkgs")
}
library(dplyr)
library(tidyr)
library(caret) # need to be installed 
```
## Load table_final 
```{r}
load("E:\\STEM-Camp\\Data\\table_final.Rdata")
```

## One more step! 

Before estimating the accuracy, we are going to create a new variable named "Response". Response is equal to 1 if your classification was correct and 0 if not. 

```{r}
table_final<-table_final%>%mutate(Response= ifelse(`Classification 1`==`Classification 2`,1,0))
```

## 1. Overall Accuracy

The first method to estimate your accuracy is such that: 

$$
\begin{aligned}
Accuracy=\frac{\text{number of correct classifications}}{\text{total number of classifications}}
\end{aligned}
$$

```{r}
acc1<-table_final%>%group_by(mediaID)%>%summarize(Accuracy=sum(Response)/15)
```

It can happen that you have classified the same image more than one time, if it's the case, Accuracy is greater than 1. Let's look at it. 

```{r}
check1<-table_final%>%group_by(mediaID)%>%tally()%>%filter(n>15)
check1
```
If check1 is empty - you haven't classified an image more than 1 time. If not, the following lines need to be run

```{r}
table_final<-table_final%>%group_by(mediaID)%>%slice(1:15)
```

```{r}
check2<-table_final%>%group_by(mediaID)%>%tally()%>%filter(n>15)
check2 # have to be 0
```

Recompute your accuracy 
```{r}
acc1<-table_final%>%group_by(mediaID)%>%summarize(Accuracy=sum(Response)/15)
```

- your maximum accuracy was 
```{r}
max(acc1$Accuracy)
```
- your minimum accuracy was 
```{r}
min(acc1$Accuracy)
```

- your average accuracy was 
```{r}
mean(acc1$Accuracy)
```

## 2. Accuracy for Hard Corals only 

```{r}
acc2<-table_final%>%group_by(mediaID)%>%filter(`Classification 1`=="Hard Corals")%>%
  summarize(Accuracy_coral=sum(Response)/n())
max(acc2$Accuracy_coral)
min(acc2$Accuracy_coral)
mean(acc2$Accuracy_coral)
```

## 3. Another approach 

A second to estimate your accuracy follows this equation:

$$
\begin{aligned}
Accuracy=\frac{\text{TP+TN}}{\text{TP+TN+FP+FN}}
\end{aligned}
$$
Where in our example: 
TP= true positives - you and the expert classified hard corals; TN= true negatives - only the expert classified hard corals, you chose something else; FP= false positives - you and the expert didn't classified hard corals; FN= false negatives - only you classified hard corals, the expert chose something else

Add TP, TN, FP and FN as variables in the table_final such as they are equal to 1 is the condition is true, 0 otherwise. 
```{r}
table_final<-table_final%>%group_by(mediaID,id)%>%filter(`Classification 1`=="Hard Corals")%>%
  mutate(TP=ifelse(`Classification 1`=="Hard Corals" & `Classification 2`=="Hard Corals",1,0))%>%
           mutate(TN=ifelse(`Classification 1`!="Hard Corals" & `Classification 2`!="Hard Corals",1,0))%>%
                    mutate(FP=ifelse(`Classification 1`!="Hard Corals" & `Classification 2`=="Hard Corals",1,0))%>%  
                             mutate(FN=ifelse(`Classification 1`=="Hard Corals" & `Classification 2`!="Hard Corals",1,0))
```

Calculate your accuracy using the equation 
```{r}
acc3<-table_final%>%group_by(mediaID)%>%summarize(Accuracy2=sum(TP+FP)/sum(TP+TN+FP+FN))
```
## 4. Another approach (again) - confusion matrix 

```{r}
tab <- table(table_final$`Classification 2`, table_final$`Classification 1`)
missings <- setdiff(colnames(tab),rownames(tab))
missing_mat <- mat.or.vec(nr = length(missings), nc = ncol(tab))
tab  <- as.table(rbind(as.matrix(tab), missing_mat))
rownames(tab) <- colnames(tab)
#matrix.f<-confusionMatrix(tab,positive="Hard Corals")
```

## 5. Questions
1. Caculate "acc3" using another the Sand category as condition, discuss about your new accuracy 
2. Explain the outputs from the confusion matrix and statistics using the R documentation - [hint] https://www.rdocumentation.org/packages/caret/versions/6.0-81/topics/confusionMatrix
3. In overall, are you ready to be a coral expert?  
