---
title: "Activity 1 - Data extraction"
author: "Julie Vercelloni"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document: default

---

<style>
table, td, th {
 border: none;
 padding-left: 1em;
 padding-right: 1em;
 min-width: 50%;
 margin-left: auto;
 margin-right: auto;
 margin-top: 1em;
 margin-bottom: 1em;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The following lines of code extract your own results from the online coral classifications database and corresponding responses from the experts. We are going to manipulate three data tables in order to join them together.

The goal is to create and save "table_final".

Details about the data tables: 

(1) "users_save.Rdata" table is composed of 2 columns. Column 1 shows the user id (in form of string) from the website, Column 2 the associated email adress with 1 row for each of you. 
(2) "elicitation_save.Rdata" table shows your classifications. It has 6 columns, including mediaID (image number), id (user id), Date (date of classification by the user), xadj and yadj (see question 2 below) and Classification 2 (classification category)
(3) "expert_save.Rdata" table is the corresponding classification by the expert. It includes 9 colums, namely id (image number), reef_name (name of the reef where the image is from), lng and lat (longitude and latitude of the image), year (year that the image was taken), xadj and yadj, and Classification (classification category)

## Load the R libraries

```{r}
rm(list=ls())
library(dplyr)
library(tidyr)

```

## Table 1

The "users_save"" table contains information about your user id and email address. The following code lines extract your user id (not known yet) based on your email address and create table 1. 

The "id" variable of table 1 is your joined field with table 2 (not created yet). 

```{r}
load("../Data/users_save.Rdata")
your_email<-"wussup111@gmail.com"
table1<-users_save%>%filter(email==your_email)%>%data.frame()
```

## Table 2

Table 2 will contain all the results from the online classification module and your associated userid and email address. A pre-manipulation was made to extract the results from the students and saved them into "elicitation_save".  

```{r}
load("../Data/elicitation_save.Rdata")
names(eli_save)
my.eli<-eli_save%>%filter(id%in%table1$id)
```
"my.eli" table can be used to look at:

- number of images that you have classified: 
```{r}
length(unique(my.eli$mediaID))
```

- number of classification per images: 
```{r}
my.eli%>%group_by(mediaID)%>%tally()
```

- number of times you classified a hard corals (hard) per images
```{r}
my.eli%>%group_by(mediaID,`Classification 2`)%>%summarise(Count=n())
```

Now we want to join my.eli and table1 together and create a new column named "Annotator 2" showing your email address 

```{r}
table2<-inner_join(my.eli,table1)
colnames(table2)<-c("mediaID","id","Date","xadj","yadj","Classification 2","Annotator 2")
```

Let's clean the factors that composed the variable "Annotator 2" for the next step. 

```{r}
table2<-table2%>%mutate(`Classification 2`=(ifelse(`Classification 2`=="hard","Hard Corals",
                                          ifelse(`Classification 2`=="algue","Algae",
                                              ifelse(`Classification 2`=="soft","Soft Corals",
                                                ifelse(`Classification 2`=="sand","Sand",
                                                       ifelse(`Classification 2`=="other","Other","Not_benthic")))))))

```

## Table 3

The last table contains the classification from the experts. 

```{r}
load("../Data/expert_save.Rdata")

table3<-exp_save%>%mutate(Classification=(ifelse(Classification=="Hard corals","Hard Corals",
                                                ifelse(Classification=="Hard Corals","Hard Corals",
                                                ifelse(Classification=="Algae","Algae",
                                                       ifelse(Classification=="Soft Coral","Soft Corals",
                                                              ifelse(Classification=="Soft Corals","Soft Corals",
                                                              ifelse(Classification=="Sand","Sand",
                                                                ifelse(Classification=="Other","Other","Not_benthic")))))))))

colnames(table3)<-c("mediaID","reef_name","lng","lat","year","Annotator1","xadj","yadj","Classification 1")
```

## Create and save the final table

Similarly to the previous step, the final table is built by joining table 2 and table 3 together. 

```{r}
table_final<-inner_join(table2,table3)
save(table_final,file="../Data/table_final.Rdata")
```

## Questions

Use table_final to answer the following questions

1. Have many unique coral reefs have you visited?    
2. Why the variables "xadj" and "yadj" are important?

## Extra question

3. Extract the total number of time that the "Annotator 1" (expert) classified "Hard Corals"