---
title: "Activity 3A - Compute the group data table"
author:
- email: j.vercelloni@qut.edu.au
  name: Julie Vercelloni
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)
```

---

<style>
table, td, th {
 border: none;
 padding-left: 1em;
 padding-right: 1em;
 min-width: 50%;
 margin-left: auto;
 margin-right: auto;
 margin-top: 1em;
 margin-bottom: 1em;
}
</style>

The following code will create a new data table for each group 

## Loading the R Libraries

```{r}
rm(list=ls())
library(dplyr)
library(tidyr)
```


## Creating Table 1

The `users_save.Rdata` table contains information about your user id and email address. The following code lines extract your user id's (not known yet) based on your email addresses and creates `table1`. 

The `id` variable of `table1` is the field used to join it with `table2` (not created yet). 

```{r}
load("../Data/users_save.Rdata")

group_emails <- c("julie.vercelloni@gmail.com","erin_test@qut.edu.au","k.mengersen@qut.edu.au") # change and add email of your group members 
table1 <- users_save %>%
  filter(email %in% group_emails) %>%
  data.frame()
```

## Creating Table 2

`table2` will contain all the results from the online classification module, your user id's, and email addresses. The results from the students were already extracted, manipulated, and saved to `elicitation_save.Rdata`.    

```{r}
load("../Data/elicitation_save.Rdata")
names(eli_save)
my.eli <- eli_save %>%
  filter(id %in% table1$id)
```


### Joining the Data

Now we want to join `my.eli` and `table1`. The table created will have a new column called `Annotator 2` that shows your email address. 

```{r}
table2 <- inner_join(my.eli, table1)
colnames(table2)<-c("mediaID",
                    "id",
                    "Date",
                    "xadj",
                    "yadj",
                    "Classification 2",
                    "Annotator 2")
```

Then we need to clean up the factors of this new variable `Annotator 2` for the next step. 

```{r}
table2 <- table2 %>% 
  mutate(`Classification 2` = case_when(`Classification 2` == "hard" ~ "Hard Corals",
                                        `Classification 2` == "algue" ~ "Algae",
                                        `Classification 2` =="soft" ~ "Soft Corals",
                                        `Classification 2` == "sand" ~ "Sand",
                                        `Classification 2` == "other" ~ "Other",
                                        TRUE ~ "Not Benthic"))
```

## Creating Table 3

The last table contains the classification from the experts. 

```{r}
load("../Data/expert_save.Rdata")

table3 <- exp_save %>% 
  mutate(Classification = case_when(Classification == "Hard corals" ~ "Hard Corals",
                                    Classification == "Hard Corals" ~ "Hard Corals",
                                    Classification == "Algae" ~ "Algae",
                                    Classification == "Soft Coral" ~ "Soft Corals",
                                    Classification == "Soft Corals" ~ "Soft Corals",
                                    Classification == "Sand" ~ "Sand",
                                    Classification == "Other" ~ "Other",
                                    TRUE ~ "Not Benthic"))

colnames(table3) <- c("mediaID",
                      "reef_name",
                      "lng",
                      "lat",
                      "year",
                      "Annotator1",
                      "xadj",
                      "yadj",
                      "Classification 1")
```

## Create and Save the Final Table

The final table `table_final` is now built by joining `table2` and `table3` together. 

```{r}
table_final <- inner_join(table2, table3)
save(table_final, file = "../Data/table_final_group.Rdata")
```