---
title: "Activity 1 - Data extraction"
author: "Julie Vercelloni"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document: default

---

<style>
table, td, th {
 border: none;
 padding-left: 1em;
 padding-right: 1em;
 min-width: 50%;
 margin-left: auto;
 margin-right: auto;
 margin-top: 1em;
 margin-bottom: 1em;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE)
```

The following lines of code extract your results from the online coral classifications database and corresponding responses from the experts. We are going to manipulate three data tables in order to join them together.

The goal is to create and save `table_final`.

Details about the data tables: 

1. `users_save.Rdata` table is composed of 2 columns.
    + Column 1 shows the user id from the website (in the form of a string), and
    + Column 2 the associated email adress with 1 row for each of you.
2. `elicitation_save.Rdata` table shows your classifications, and it has 6 columns including
    + mediaID (image number),
    + id (user id),
    + Date (date of classification by the user),
    + xadj and yadj (see question 2 below), 
    + and Classification 2 (classification category).
3. `expert_save.Rdata` table is the corresponding classification by the expert, and it has 9 columns including
    + id (image number),
    + reef_name (name of the reef where the image is from),
    + lng and lat (longitude and latitude of the image),
    + year (year that the image was taken),
    + xadj and yadj, and
    + Classification (classification category)

## Loading the R Libraries

```{r}
rm(list=ls())
library(dplyr)
library(tidyr)
```

## Creating Table 1

The `users_save.Rdata` table contains information about your user id and email address. The following code lines extract your user id (not known yet) based on your email address and create `table1`. 

The `id` variable of `table1` is the field used to join it with `table2` (not created yet). 

```{r}
load("../Data/users_save.Rdata")
your_email <- "wussup111@gmail.com"
table1 <- users_save %>%
  filter(email==your_email) %>%
  data.frame()
```


## Creating Table 2

`table2` will contain all the results from the online classification module, your user id, and email address. The results from the students were already extracted, manipulated, and saved to `elicitation_save.Rdata`.  

```{r}
load("../Data/elicitation_save.Rdata")
names(eli_save)
my.eli <- eli_save %>%
  filter(id %in% table1$id)
```

### Inspecting Your Data

You can use the `my.eli` table to look at:

- the number of images you have classified: 
```{r}
length(unique(my.eli$mediaID))
```
- the number of classifications per image: 
```{r}
my.eli %>%
  group_by(mediaID) %>%
  tally()
```
- the number of times you classified a point as hard coral (`hard`) per image:
```{r}
my.eli %>% 
  group_by(mediaID, `Classification 2`) %>% 
  summarise(Count = n())
```

### Joining the Data

Now we want to join `my.eli` and `table1`. The table created will have a new column called `Annotator 2` that shows your email address. 

```{r}
table2 <- inner_join(my.eli, table1)
colnames(table2)<-c("mediaID", 
                    "id", 
                    "Date", 
                    "xadj", 
                    "yadj",
                    "Classification 2",
                    "Annotator 2")
```

Then we need to clean up the factors of this new variable `Annotator 2` for the next step. 

```{r}
table2 <- table2 %>% 
  mutate(`Classification 2` = case_when(`Classification 2` == "hard" ~ "Hard Corals",
                                        `Classification 2` == "algue" ~ "Algae",
                                        `Classification 2` =="soft" ~ "Soft Corals",
                                        `Classification 2` == "sand" ~ "Sand",
                                        `Classification 2` == "other" ~ "Other",
                                        TRUE ~ "Not Benthic"))

```

## Creating Table 3

The last table contains the classification from the experts. 

```{r}
load("../Data/expert_save.Rdata")

table3 <- exp_save %>% 
  mutate(Classification = case_when(Classification == "Hard corals" ~ "Hard Corals",
                                    Classification == "Hard Corals" ~ "Hard Corals",
                                    Classification == "Algae" ~ "Algae",
                                    Classification == "Soft Coral" ~ "Soft Corals",
                                    Classification == "Soft Corals" ~ "Soft Corals",
                                    Classification == "Sand" ~ "Sand",
                                    Classification == "Other" ~ "Other",
                                    TRUE ~ "Not Benthic"))

colnames(table3) <- c("mediaID",
                      "reef_name",
                      "lng",
                      "lat",
                      "year",
                      "Annotator1",
                      "xadj",
                      "yadj",
                      "Classification 1")
```

## Create and Save the Final Table

The final table `table_final` is now built by joining `table2` and `table3` together. 

```{r}
table_final <- inner_join(table2, table3)
save(table_final, file = "../Data/table_final.Rdata")
```

## Questions

Use `table_final` to answer the following questions

1. Have many unique coral reefs have you visited?    
2. Why are the variables `xadj` and `yadj` important?

### Extra question

3. How many times did the expert `Annotator1` classify `Hard Corals`?