---
title: "Activity 3 -Visualisation"
author: "Julie Vercelloni"
date: "1 April 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

We are now interested to visualise your results. Using the ggplot2 package, we are going to produce 2 plots. The first plot will show your effort in image classifications and the second plot your associated accuracy.

This activity is in group - you need to rerun Activity 1 to combine all responses of your group members and save another table named table_final_group 

##Load the R libraries

```{r}
rm(list=ls())

julie <- Sys.info()["nodename"] == "SEF-PA00130783"

if (julie){
  .libPaths("C:\\Julie\\Rpkgs")
}
library(dplyr)
library(tidyr)
library(ggplot2)
library(caret) # need to be installed 
```
## Load data 
```{r}
load("E:\\STEM-Camp\\Data\\table_final_group.Rdata")
```

```{r}
table_final<-table_final_group%>%mutate(Response= ifelse(`Classification 1`==`Classification 2`,1,0))%>%
  group_by(mediaID,id)%>%slice(1:15)
```

## 1. Recompute accuracy 

-Overall Accuracy

```{r}
acc1<-table_final%>%group_by(mediaID,id)%>%summarize(Accuracy=sum(Response)/15)
```

- Accuracy for Hard Corals only 

```{r}
acc2<-table_final%>%group_by(mediaID,id)%>%filter(`Classification 1`=="Hard Corals")%>%
  summarize(Accuracy_coral=sum(Response)/n())
```

## 2. Your turn - realise the 2 plots
1. Discuss with your group what do you want to show in plot 1 and 2
2. Sketchup plot 1 and 2 on a piece of paper 
3. Use ggplot2 to make the graphs - Alan, Ella and Grace will help you! 


