---
title: "Activity 3A - Compute the group data table"
author: "Julie Vercelloni"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---

<style>
table, td, th {
 border: none;
 padding-left: 1em;
 padding-right: 1em;
 min-width: 50%;
 margin-left: auto;
 margin-right: auto;
 margin-top: 1em;
 margin-bottom: 1em;
}
</style>

The following code will create the new data table per group 

##Step 1 - Load the R libraries

```{r}
rm(list=ls())
library(dplyr)
library(tidyr)
```


##Step 2 - Creation of table 1

The "users_save"" table contains information about your user id and email address. The following code lines extract your user id (not known yet) based on your email address and create table 1. 

The "id" variable of table 1 is your joined field with table 2 (not created yet). 

```{r}
load("../Data/users_save.Rdata")

group_emails<- c("lucas.welker@student.education.wa.edu.au","iriedaniellee@gmail.com","ihaa4t@gmail.com")
table1<-users_save%>%filter(email%in%group_emails)%>%data.frame()
```

##Step 3 - Creation of table 2

The table 2 will contain all the results from the online classification module and your associated userid and email address. 
A pre-manipulation was made to extract the results from the students and saved them into "elicitation_save".  

```{r}
load("../Data/elicitation_save.Rdata")
names(eli_save)
my.eli<-eli_save%>%filter(id%in%table1$id)
```

Now we want to join my.eli and table1 together and create a new column named "Annotator 2" showing your email address 

```{r}
table2<-inner_join(my.eli,table1)
colnames(table2)<-c("mediaID","id","Date","xadj","yadj","Classification 2","Annotator 2")
```

Let's clean the factors that composed the variable "Annotator 2" for the next step. 

```{r}
table2<-table2%>%mutate(`Classification 2`=(ifelse(`Classification 2`=="hard","Hard Corals",
                                          ifelse(`Classification 2`=="algue","Algae",
                                              ifelse(`Classification 2`=="soft","Soft Corals",
                                                ifelse(`Classification 2`=="sand","Sand",
                                                       ifelse(`Classification 2`=="other","Other","Not_benthic")))))))

```

##Step 4 - Creation of table 3

The last table contains the classification from the experts. 

```{r}
load("../Data/expert_save.Rdata")

table3<-exp_save%>%mutate(Classification=(ifelse(Classification=="Hard corals","Hard Corals",
                                                ifelse(Classification=="Hard Corals","Hard Corals",
                                                ifelse(Classification=="Algae","Algae",
                                                       ifelse(Classification=="Soft Coral","Soft Corals",
                                                              ifelse(Classification=="Soft Corals","Soft Corals",
                                                              ifelse(Classification=="Sand","Sand",
                                                                ifelse(Classification=="Other","Other","Not_benthic")))))))))

colnames(table3)<-c("mediaID","reef_name","lng","lat","year","Annotator1","xadj","yadj","Classification 1")
```

##Step 5 - Create and save the final table

Similarly the previous step, the final table is built by joining table 2 and table 3 together. 


```{r}
table_final_group<-inner_join(table2,table3)
save(table_final_group,file="../Data/table_final_group.Rdata")
```