---
title: "Activity 3 -Visualisation"
author: "Julie Vercelloni"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)
```

This activity is to be done in a group so you need to run \textbf{Activity 3A} to combine the responses of your group members and save another table named `table_final_group.Rdata`.

We are now interested in visualising your results. We will use the `ggplot2` package to produce two plots:
1. The first plot will show your effort in classifying images whether individually, per group, or for everyone.
2. The second plot will show some measure of accuracy whether individually, per group, or for everyone. 

## Loading the R Libraries

```{r}
rm(list=ls())
library(dplyr)
library(tidyr)
library(ggplot2)
library(caret) # need to be installed 
```

## Loading the Data 

```{r}
load("../Data/table_final_group.Rdata")
```

```{r}
table_final <- table_final %>% 
  mutate(Response = ifelse(`Classification 1` == `Classification 2`, 1, 0)) %>%
  group_by(mediaID, id) %>% 
  slice(1:15)
```

## Overall Accuracy 

```{r}
acc1 <- table_final %>%
  group_by(mediaID, id) %>% 
  summarize(Accuracy = sum(Response) / 15)
```

## Accuracy When Identifying Hard Corals

```{r}
acc2 <- table_final %>% 
  group_by(mediaID, id) %>%
  filter(`Classification 1` == "Hard Corals") %>%
  summarize(Accuracy_coral = sum(Response) / n())
```

## Questions

1. Discuss within your group what you want to show in plot 1 and 2 **(~ 20min)**
2. As a group, describe what you will be showing - each group should present something different **(~ 10min)**
3. Sketch plot 1 and 2 by hand on a piece of paper **(~ 30min)**
4. Use `ggplot2` to make the graphs - we will help you! 