---
title: "Activity 2 - Estimates of accuracy"
author:
- email: j.vercelloni@qut.edu.au
  name: Julie Vercelloni
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)
```

---

<style>
table, td, th {
 border: none;
 padding-left: 1em;
 padding-right: 1em;
 min-width: 50%;
 margin-left: auto;
 margin-right: auto;
 margin-top: 1em;
 margin-bottom: 1em;
}
</style>

Using `table_final` from Activity 1, we will calculate your accuracy when classifying images. Depending on your research question, there can be many different ways to do this.   

## Loading the R Libraries

```{r}
rm(list=ls())
library(dplyr)
library(tidyr)
library(caret) # need to be installed 
```

### Loading the Data

```{r}
load("../Data/table_final.Rdata")
```

## Creating the Response Variable  

In order to estimate your accuracy, we first need to create a new variable named `Response` which is

* equal to 1 if you correctly classified the point, and 
* equal to 0 if not. 

```{r}
table_final <- table_final %>%
  mutate(Response = ifelse(`Classification 1` == `Classification 2`, 1, 0))
```

## Overall Accuracy

The first method we will use to estimate your accuracy is calculated using the formula

$$
\text{Accuracy}=\frac{\text{number of correct classifications}}{\text{total number of classifications}}
$$

```{r}
acc1 <- table_final %>%
  group_by(mediaID) %>% 
  summarize(Accuracy = sum(Response) / 15)
```

However, you could have classified the same image more than once. If this has happened, your calculated accuracy will be greater than 1. Let's have a look and see how to fix it. 

```{r}
check1 <- table_final %>% 
  group_by(mediaID) %>% 
  tally() %>% 
  filter(n > 15)

check1 %>% 
  select(mediaID)
```

The results from `check1` are the media IDs of images you have classified more than once. If there are results printed, the following lines need to be run

```{r}
table_final <- table_final %>% 
  group_by(mediaID) %>% 
  slice(1:15)
```

```{r}
check2 <- table_final %>% 
  group_by(mediaID) %>% 
  tally() %>% 
  filter(n>15)
check2 %>%
  select(mediaID) # empty
```

If `check1` was empty, that means you didn't classfy any image more than once. If `check1` had some results, after running the above code, `check2` should return nothing.

### Recomputing Your Accuracy

Now that we have made sure you have only one classification for each image, we need to recalculate your accuracy.

```{r}
acc1 <- table_final %>%
  group_by(mediaID) %>%
  summarize(Accuracy = sum(Response) / 15)
```

- your maximum accuracy was, 
```{r}
max(acc1$Accuracy)
```
- your minimum accuracy was, and
```{r}
min(acc1$Accuracy)
```
- your average accuracy was 
```{r}
mean(acc1$Accuracy)
```

## Accuracy When Identifying Hard Corals 

However we might want to know how good you are at classifying `Hard Corals`, so we are now going to calculate your accuracy for a specific classification we are interested in.

```{r}
acc2 <- table_final %>%
  group_by(mediaID) %>%
  filter(`Classification 1` == "Hard Corals") %>%
  summarize(Accuracy_coral = sum(Response) / n())

max(acc2$Accuracy_coral)
min(acc2$Accuracy_coral)
mean(acc2$Accuracy_coral)
```

## Confusion matrix 

```{r}
tab <- table(table_final$`Classification 2`,
             table_final$`Classification 1`)
missings<-abs(length(rownames(tab))-length(colnames(tab)))

if (length(rownames(tab))>length(colnames(tab))){
missing_mat <- mat.or.vec(nr = length(missings),
                          nc = nrow(tab))
tab  <- as.table(cbind(as.matrix(tab),
                       t(missing_mat))) 

r.tab<-rownames(tab)
colnames(tab) <- c(r.tab[rownames(tab)%in%colnames(tab)==TRUE],r.tab[rownames(tab)%in%colnames(tab)==FALSE])
tab<-tab[match(rownames(tab),colnames(tab)),]

}else{
missing_mat <- mat.or.vec(nr = length(missings),
                          nc = nrow(tab))
tab  <- as.table(rcbind(as.matrix(tab),
                       missing_mat)) 

c.tab<-rownames(tab)
colnames(tab) <- c(c.tab[colnames(tab)%in%rownames(tab)==TRUE],c.tab[colnames(tab)%in%rownames(tab)==FALSE])
tab<-tab[match(colnames(tab),rownames(tab)),]
}


matrix.f <- confusionMatrix(tab, positive="Hard Corals") # remove the hash in front of matrix.f
matrix.f
```

## Questions
1. Calculate `acc2` using another factor level, such as `Sand`, as the classification of interest and discuss your accuracy.
2. Formulate a research question that could be answered using `acc2` for `Hard Corals` and `Sand`? 
2. Explain the outputs from the confusion matrix and statistics using the R documentation ([click here for a hint](https://www.rdocumentation.org/packages/caret/versions/6.0-81/topics/confusionMatrix))
3. Overall, are you ready to be a coral expert?  

## Extra 

A third way to estimate your accuracy uses the following calculation

$$
\text{Accuracy}=\frac{\text{TP + TN}}{\text{TP + TN + FP + FN}}
$$
where

* TP are true positives, you and the expert correctly classified hard corals; 
* TN are true negatives, the expert correctly classified hard corals but you chose something else;
* FP are false positives, you and the expert incorrectly classified hard corals; 
* FN are false negatives, only you correctly classified hard corals but the expert chose something else.

Add `TP`, `TN`, `FP` and `FN` as variables in `table_final` such that they are

* equal to 1 is the condition is true, and
* equal to 0 otherwise.

```{r}
table_final <- table_final %>% 
  group_by(mediaID,id) %>% 
  filter(`Classification 1` == "Hard Corals") %>%
  mutate(TP = ifelse(`Classification 1` == "Hard Corals" & `Classification 2` == "Hard Corals", 1, 0)) %>%
  mutate(TN = ifelse(`Classification 1` != "Hard Corals" & `Classification 2` != "Hard Corals", 1, 0)) %>%
  mutate(FP = ifelse(`Classification 1` != "Hard Corals" & `Classification 2` == "Hard Corals", 1, 0)) %>%
  mutate(FN = ifelse(`Classification 1` == "Hard Corals" & `Classification 2` != "Hard Corals", 1, 0))
```

Now we can calculate your accuracy using the previous equation

```{r}
acc3 <- table_final %>% 
  group_by(mediaID) %>% 
  summarize(Accuracy2 = sum(TP + FP) / sum(TP + TN + FP + FN))
```