---
title: "Activity 3 -Visualisation"
author: "Julie Vercelloni"
date: "1 April 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This activity is in group - you need to run Activity 3A to combine all responses of your group members and save another table named table_final_group 

We are now interested to visualise your results. Using the ggplot2 package, we are going to produce 2 plots:
1. The first plot will show your effort in image classifications, it can be individual, per group or everyone
2. The second plot will show some aspects of accuracy, it can be individual, per group or everyone. 

##Load the R libraries

```{r}
rm(list=ls())

julie <- Sys.info()["nodename"] == "SEF-PA00130783"

if (julie){
  .libPaths("C:\\Julie\\Rpkgs")
}
library(dplyr)
library(tidyr)
library(ggplot2)
library(caret) # need to be installed 
```
## Load data 
```{r}
load("E:\\STEM-Camp\\Data\\table_final_group.Rdata")
```

```{r}
table_final<-table_final_group%>%mutate(Response= ifelse(`Classification 1`==`Classification 2`,1,0))%>%
  group_by(mediaID,id)%>%slice(1:15)
```

## Recompute accuracy 

- Overall Accuracy

```{r}
acc1<-table_final%>%group_by(mediaID,id)%>%summarize(Accuracy=sum(Response)/15)
```

- Accuracy for Hard Corals only 

```{r}
acc2<-table_final%>%group_by(mediaID,id)%>%filter(`Classification 1`=="Hard Corals")%>%
  summarize(Accuracy_coral=sum(Response)/n())
```

## Questions
1. Discuss with your group what do you want to show in plot 1 and 2 ~ 20min
2. Explain to everyone - each group should describe something different ~ 10min
3. Sketchup plot 1 and 2 on a piece of paper ~ 30min
4. Use ggplot2 to make the graphs - we will help you! 


